Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-11 papers/marlowe2019/paper.tex
Use pdf for figures for vector graphics

\begin{figure}[!h]
    \centering
    \includegraphics[width=4in]{figures/Marlowe3-Figures-003.jpeg}
    \caption{Cardano EUTx0 Model}
    \label{fig:eutxo}
\end{figure}

@@

\noindent%SJT: **general question** using \emph for inline code: why not \texttt ?
where \texttt{accounts} maps account ids to their balances, \texttt{choices} stores user made choice values,
\texttt{boundValues} stores evalutated \texttt{Value}'s introduced by \texttt{Let} expressions,
and \texttt{minSlot} holds a minimal slot number that a contract has seen, to avoid `time travel to the past'.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/Marlowe3-Figures-004.jpeg}
    \caption{Zero Coupon Bond Contract}
    \label{fig:zero-coupon-bond}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=4in]{figures/Marlowe3-Figure-1-crop.pdf}
    \caption{Cardano EUTx0 Model}
    \label{fig:eutxo}
\end{figure}

@@

\noindent
where \texttt{accounts} maps account ids to their balances, \texttt{choices} stores user made choice values,
\texttt{boundValues} stores evalutated \texttt{Value}'s introduced by \texttt{Let} expressions,
and \texttt{minSlot} holds a minimal slot number that a contract has seen, to avoid `time travel to the past'.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=4in]{figures/Marlowe3-Figure-2-crop.pdf}
    \caption{Zero Coupon Bond Contract}
    \label{fig:zero-coupon-bond}
\end{figure}
